---
title: "p8105_hw2_bp2678"
author: "Brady Pham"
date: 2023-10-04
output: github_document
---
```{r}
library(tidyverse)

```


#Question 2

Mr Trash wheel; clean data set 

```{r}
mr_trash_df = 
  readxl::read_excel("Data/202309 Trash Wheel Collection Data.xlsx", 
  sheet = 1, range = "A2:N586") |>
  janitor::clean_names() |>
  mutate(homes_power = (weight_tons*500/30),
        trash_df = "mr_trash", 
        year = as.numeric(year)) |>
  relocate(trash_df)
```

Professor Trash Wheel; clean data set 

```{r}
Professor_trash_df = 
  readxl::read_excel("Data/202309 Trash Wheel Collection Data.xlsx", 
  sheet = 2, range = "A2:M108") |>
  janitor::clean_names() |>
  mutate(homes_power = (weight_tons*500/30),
         trash_df = "professor_trash") |>
  relocate(trash_df)
```

Gwynnda Trash Wheel; clean data set 

```{r}
Gwynndar_trash_df = 
  readxl::read_excel("Data/202309 Trash Wheel Collection Data.xlsx", 
  sheet = 4, range = "A2:L157") |>
  janitor::clean_names() |>
  mutate(homes_power = (weight_tons*500/30),
         trash_df = "Gwynndar_trash") |>
  relocate(trash_df)
Gwynndar_Cigs_butt = Gwynndar_trash_df[1,10] + Gwynndar_trash_df[2,10] + Gwynndar_trash_df[3,10] + Gwynndar_trash_df[4,10] + Gwynndar_trash_df[5,10]

```

Total of all the trash wheel

```{r}
Total_trash_df =
  bind_rows(Gwynndar_trash_df, Professor_trash_df, mr_trash_df)
```

In the dataset of Mr. Trash Wheel, it had three different data set for Mr. Trash Wheel, Professor Trash Wheel, and Gwnnda Trash wheel. In those three data set they had a total observation of 846. Professor Trash Wheel had a total of 216.26 tons collected and Gwynnda collected a total of 16300 cigarette butts in July 2021. 

#Question 3

```{r}
baseline_mci_df = 
  read_csv("data/MCI_baseline.csv", skip = 1) |>
  janitor::clean_names() |>
  mutate(
    sex = recode(
      sex,
      `1` = "male",
      `0` = "female")) |>
  mutate(
  apoe4 = recode(
    apoe4,
    `1` = "carrier",
    `0` = "non-carrier"))
 
```






